### 2010-11-29 docs/tex/result.tex
Changed the name of the chapters.
Small updates
Some Quotations Added
Modified with Dr. Grogono's comments

% All the result and analysis
\chapter{Results and Analysis}

@@

\begin{table}[H]
\centering
\begin{tabular}{| p{2cm} | >{\centering} p{2.2cm} | p{8cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
	\hline
\end{tabular}
\caption{Parameters to Mimicry Ring Report.}
\label{tab:ring-report-control-parameters}
\end{table}

@@

The memory configuration size for predators are a very interesting parameter. The minimum memory size is directly associated with the number of prey species with which we initiate the simulation. Otherwise evolution of mimicry is not observed. As mentioned in Table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species. After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgement. At this point its memory size is zero. As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank. No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species. When catching a prey if its memory tells that it is palatable, it will consume that prey. Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.

Now as we know the behaviour of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory. So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern previously captured and the patterns stored in memory.

% Put the image
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/simTime10k-2Prey}
	\caption{Population distribution of mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey}
\end{figure}

@@

%Put the number of rings picture:
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
	\caption{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

@@

%Screenshot of the simulation
\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime7600-2-prey}
	\includegraphics[scale=0.55]{images/simTime7600}
	\caption{Graphical representation of the model, simulation time: 7600.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
	\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
	\label{fig:plot-4-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
	\caption{Number of mimicry rings, initialized with 4 prey species.}
	\label{fig:ringSize10k-4Prey}
\end{figure}

\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime11K-4Prey}
	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
	\caption{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime9K-4MorePrey}
	\caption{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:plot-4-more-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4MorePrey}
	\caption{Number of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:ringSize10k-4MorePrey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-6Prey}
	\caption{Population distribution of mimicry rings, initialized with 6 prey species.}
	\label{fig:plot-6-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
	\caption{Number of mimicry rings, initialized with 6 prey species.}
	\label{fig:ringSize10k-6-Prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-unp}
	\caption{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize9k-4Prey-unp}
	\caption{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:ringSize10k-4-Prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
	\caption{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
	\caption{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
	\caption{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:plot-1-prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
	\caption{Number of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:ringSize8k-1-Prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime9k-1-p}
	\caption{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
	\label{fig:plot-1-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
	\caption{Number of mimicry rings, initialized with 1 palatable prey species.}
	\label{fig:ringSize8k-1-Prey-p}
\end{figure}

>>>>

% All the result and analysis
\chapter{The Results}

\begin{quote}
\textsl{``The most incomprehensible thing about the world is that it is comprehensible." - Albert Einstein}
\end{quote}

@@

\begin{table}[H]
\centering
\begin{tabular}{| p{2cm} | >{\centering} p{2.2cm} | p{8cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
	\hline
\end{tabular}
\caption{Parameters to mimicry ring report.}
\label{tab:ring-report-control-parameters}
\end{table}

@@

The memory configuration size for predators is a very interesting parameter. The minimum memory size is directly associated with the number of prey species with which we initiate the simulation. Otherwise evolution of mimicry is not observed. As mentioned in Table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species. After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment. At this point its memory size is zero. As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank. No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species. When catching a prey if its memory tells that it is palatable, it will consume that prey. Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.

Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory. So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern previously captured and the patterns stored in memory.

% Put the image
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species)]{Population distribution of mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey}
\end{figure}

@@

%Put the number of rings picture:
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

@@

%Screenshot of the simulation
\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime7600-2-prey}
	\includegraphics[scale=0.55]{images/simTime7600}
	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
	\label{fig:plot-4-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
	\label{fig:ringSize10k-4Prey}
\end{figure}

\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime11K-4Prey}
	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
	\caption[Graphical representation of the model (simulation time: 11200)]{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime9K-4MorePrey}
	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:plot-4-more-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4MorePrey}
	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:ringSize10k-4MorePrey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-6Prey}
	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
	\label{fig:plot-6-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
	\label{fig:ringSize10k-6-Prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-unp}
	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize9k-4Prey-unp}
	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:ringSize10k-4-Prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:plot-1-prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:ringSize8k-1-Prey-unp}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime9k-1-p}
	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
	\label{fig:plot-1-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
	\label{fig:ringSize8k-1-Prey-p}
\end{figure}

### 2010-11-29 docs/tex/review.tex
Modified with Dr. Grogono's comments

\begin{quote}
``The theory of evolution by cumulative natural selection is the only theory we know of that is in principle capable of explaining the existence of organized complexity" - Richard Dawkins \cite{dawkins1996}
\end{quote}

@@

``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}

@@

\paragraph{Turing(1948)}
Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled ``Intelligent Machinery" where the expression of ``genetical or evolutionary search"  was used \cite{turing1948}. He suggested a range of ideas for systems which could be said to modify their own programs.

@@

\paragraph{L. Fogel, Owens and Walsh (1965)}
A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in ``Artificial Intelligence through a simulation of evolution" \cite{fogel1966}. In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series. Evolutionary prediction of such kind was motivated by the concept that prediction is a keystone to intelligent behavior (defined in terms of adaptive behavior, in that the intelligent organism must anticipate events in order to adapt behavior in light of a goal).

\paragraph{Holland(1975)}
Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H. Holland. His ground breaking book ``Adaptation in natural and artificial systems" \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.

\paragraph{Koza(1992)}
Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem. Starting from a high-level statement of ``what needs to be done" it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.

@@

\begin{itemize}
	\item ``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."
	\item ``Selection acts as a force pushing quality."
\end{itemize}

@@

\paragraph{Variation operators, recombination and mutation}
Considering arity (number of object as input) variation operators are divided into two kinds. The mutation operator accepts only one operand. The process of mutation is similar to the way it happens in biology. It is a stochastic process, meaning, its output the child depends on the outcomes of a series of random choices. The operator is responsible for causing a random unbiased change. Mutation has very different roles in different fields of EC, for example in Genetic Programming it is not used at all, while in genetic algorithms it is a very pivotal process as it provides fresh blood to the existing set of solutions. Getting a new mutated child is like stepping into a new solution space outside of the ones which already exist in the parent pool. A recombination operator is responsible for merging two parent genotypes into one or two offspring genotypes. It is also a stochastic process depending on the choice of the parts of the parent individuals. Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent. According to Eiben \cite{eiben2003} ``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features." It is important that variation operators are defined based on the representation of the problem under consideration.

@@

\section{Artificial Life}
As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that in Artificial Life scientist take concepts from Biology specially Evolutionary Biology and genetics and implement into computer science.

@@

\begin{quote}
`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."
\end{quote}

\section{History}

>>>>

\begin{quote}
\textsl{``The theory of evolution by cumulative natural selection is the only theory we know of that is in principle capable of explaining the existence of organized complexity" - Richard Dawkins \cite{dawkins1996}}
\end{quote}

@@

\textsl{``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}}

@@

\paragraph{Turing(1948)}
Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled \textsl{``Intelligent Machinery"} where the expression of \textsl{``genetical or evolutionary search"}  was used \cite{turing1948}. He suggested a range of ideas for systems which could be said to modify their own programs.

@@

\paragraph{L. Fogel, Owens and Walsh (1965)}
A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in \textsl{``Artificial Intelligence through a simulation of evolution"} \cite{fogel1966}. In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series. Evolutionary prediction of such kind was motivated by the concept that prediction is a keystone to intelligent behavior (defined in terms of adaptive behavior, in that the intelligent organism must anticipate events in order to adapt behavior in light of a goal).

\paragraph{Holland(1975)}
Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H. Holland. His ground breaking book \textsl{``Adaptation in natural and artificial systems"} \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.

\paragraph{Koza(1992)}
Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem. Starting from a high-level statement of \textsl{``what needs to be done"} it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.

@@

\begin{itemize}
	\item \textsl{``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."}
	\item \textsl{``Selection acts as a force pushing quality."}
\end{itemize}

@@

\paragraph{Variation operators, recombination and mutation}
Considering arity (number of object as input) variation operators are divided into two kinds. The mutation operator accepts only one operand. The process of mutation is similar to the way it happens in biology. It is a stochastic process, meaning, its output the child depends on the outcomes of a series of random choices. The operator is responsible for causing a random unbiased change. Mutation has very different roles in different fields of EC, for example in Genetic Programming it is not used at all, while in genetic algorithms it is a very pivotal process as it provides fresh blood to the existing set of solutions. Getting a new mutated child is like stepping into a new solution space outside of the ones which already exist in the parent pool. A recombination operator is responsible for merging two parent genotypes into one or two offspring genotypes. It is also a stochastic process depending on the choice of the parts of the parent individuals. Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent. According to Eiben \cite{eiben2003} \textsl{``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features."} It is important that variation operators are defined based on the representation of the problem under consideration.

@@

\section{Artificial Life}
As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that in Artificial Life scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.

@@

\begin{quote}
\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment." - Christopher G. Langton}
\end{quote}

%\section{History}
